Containers and R---the Rockerverse and beyond

### 2020-01-16 manuscript.Rmd
one sentence per line in compendia draft

- researchcompendia.science
- https://github.com/benmarwick/rrtools

@@

- \pkg{renv}, https://rstudio.github.io/renv/articles/docker.html
- what to copy in and what not

>>>>

@@

- Website researchcompendia.science
- Gentlemen
- R and friends (what do they recommend)
- rrtools - https://github.com/benmarwick/rrtools
- Some concrete examples, incl. Madjebe 
- \pkg{renv}, https://rstudio.github.io/renv/articles/docker.html
- what to copy in and what not
